\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=-0.1in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\usepackage{hyperref} % For hyperlinks
\usepackage{fontawesome} % For icons
\usepackage{xcolor} % For color customization

% Define color for contact information
\definecolor{contactcolor}{HTML}{0000FF} % Blue color for phone number and email

\begin{document}

% Contact information
\noindent
\begin{minipage}[c]{\textwidth}
    \centering
    {\huge \scshape Sankar Rayi} \\ % Name without \vspace{}
    \vspace{5pt} % Adjust the spacing here as needed
    \textcolor{contactcolor}{\raisebox{-0.1\height}{\faPhone\ +91 7032986458}} \hspace{10pt}
    \textcolor{contactcolor}{\href{mailto:rayisankar8888@gmail.com}{\faEnvelope\  rayisankar8888@gmail.com}} \hspace{10pt}
    \textcolor{contactcolor}{\href{https://github.com/SmartSankarCode}{\faGithub\  GitHub}}
\end{minipage}

% OBJECTIVE
\begin{rSection}{Objective}
Aspiring Full-Stack Developer with a keen interest in Artificial Intelligence. Passionate about creating innovative, user-friendly applications and exploring AI-driven solutions to enhance modern software development. Eager to contribute to impactful projects and grow within a dynamic team.
\end{rSection}

% EDUCATION SECTION
\begin{rSection}{Education}
{\bf B.Tech in EEE}, Sir C.R. Reddy College of Engineering(JNTUK), Eluru \hfill{\bf 2020 - 2024} \\
CGPA: 6.93 \hfill AP, India

{\bf Intermediate (MPC)}, Sir C.R. Reddy Autonomous College \hfill {\bf 2018 - 2020} \\
CGPA: 6.90 \hfill AP, India
\end{rSection}


% SKILLS SECTION
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{5ex}} p{0.7\textwidth} }
Programming Languages & Python, HTML, CSS, JavaScript \\
Frameworks/Libraries & React.js, Express.js \\
Databases & MongoDB, MySQL \\
Developer Tools & Git/Github, VS Code, Anaconda \\
Certifications & Python (Cisco), JavaScript, React.js (GeeksforGeeks), 
SQL \href{https://www.linkedin.com/in/smartsankarcode3399/details/certifications/}{(View)} \\

\end{tabular}

\end{rSection}
 % Reduces space by one line

% PROJECTS SECTION
\begin{rSection}{Projects}

\textbf{Full-Stack E-commerce Application (MERN Stack)}
\begin{itemize}
    \itemsep -7pt
    \item Developed an e-commerce site with product browsing, cart management, checkout, and a complete order management system, enhancing system efficiency and user experience across devices.
    \item Built secure backend APIs using Node.js, Express.js, MongoDB, with JWT-based authentication in HTTP-only cookies, integrated with a responsive React.js frontend.
    \item Implemented key features such as user authentication, order lifecycle management, and order tracking, enhancing security, reliability, and usability.
    \item Deployed backend on Render and frontend on Netlify, ensuring scalability and accessibility, with API integration and Git/GitHub version control.
     \href{https://github.com/SmartSankarCode/ecommerce.git}{(Project Link)}
\end{itemize}

\textbf{Amazon Frontend Application (HTML, CSS, JavaScript)}
\begin{itemize}
    \itemsep -7pt
    \item Designed and developed an amazon frontend with product grid, dynamic search, cart functionality, and order management, ensuring seamless navigation, usability, and cross-device compatibility.
    \item Integrated a mock API for product data and order simulation, enabling real-time order tracking and purchase history, while improving testing workflows.
    \item Gained hands-on experience in frontend development, API integration, responsive layouts, and custom logic implementation.
     \href{https://github.com/SmartSankarCode/Interactive-Amazon-Project.git}{(Project Link)}
\end{itemize}

\textbf{Netflix UI Clone (HTML, CSS)}
\begin{itemize}
    \itemsep -7pt
    \item Created a pixel-perfect static clone of the Netflix homepage including navigation, hero section, and content grid.
    \item Utilized CSS Flexbox and Grid to build a responsive layout that adapts flawlessly across devices, improving expertise in UI development, responsive design, and layout structuring.
     \href{https://github.com/SmartSankarCode/flixNet-OTT-UI-2025.git}{(Project Link)}
\end{itemize}

\end{rSection}



% EXTRA-CURRICULAR ACTIVITIES SECTION
\begin{rSection}{Extra-Curricular Activities}
\begin{itemize}
    \itemsep -7pt
    \item Volunteered in an Arduino workshop organized by the IETE Student Forum, gaining exposure to hardware programming and event coordination.
    \item Attended a remote AI Summer Internship organized by 1Stop, gaining practical exposure to Artificial Intelligence concepts and applications.
   

\end{itemize}
\end{rSection}


\end{document}
